Dominance Regions for Rank Two Cluster Algebras

### 2022-04-07 dominance_regions.tex
Some section 4 edits

    For $k=2j$, $j>0$, and $\lambda\in\cI$, we observe that $\cC_k(\phi_k\lambda)\subset\RR^2$ is given by the inequalities 
    \[ x - u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \le 0 \qquad\text{and}\qquad 0 \le y + u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
    \[ (\dagger)\ x\le u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2 \qquad\text{and}\qquad (\ddagger)\ -y\le u_{2j,-}\lambda_1+u_{2j-1,-}\lambda_2. \]
    We inductively compute the region $\phi_{2j}^{-1}\cC_{2j}(\phi_{2j}\lambda)$, using Lemma~\ref{le:transformed inequalities} and the equality $\phi_{2j}^{-1}=\phi_2^{-j}$.

@@

    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2^{-1}$.
    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
    \[u_{2i+2,-}x+u_{2i+1,+}y=(u_{3,+}u_{2i,-}-u_{2,-}u_{2i-1,+})x+(u_{2,+}u_{2i,-}-u_{1,-}u_{2i-1,+})y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2,\]
    which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
    \[-u_{2i+1,-}x-u_{2i,+}y=(-u_{3,+}u_{2i-1,-}+u_{2,-}u_{2i-2,+})x+(-u_{2,+}u_{2i-1,-}+u_{1,-}u_{2i-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
    \[u_{2i+3,-}x+u_{2i+2,+}y=(u_{3,+}u_{2i+1,-}-u_{2,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (b) for $i+1$.
    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
    \[-u_{2i+1,-}x-u_{2i,+}y=(u_{1,+}u_{2i-1,-}-u_{2,-}u_{2i,+})x+(-u_{0,+}u_{2i-1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
    \[-u_{2i+1,-}x+u_{2i+2,+}y=(-u_{1,+}u_{2i+1,-}+u_{0,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
    \[-u_{2i+1,-}x-u_{2i,+}y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
    This completes the induction on $i$, proving the Claim and the result for $k$ even.

>>>>

@@

    Assuming the inequalities (a)-(d) hold for $i$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_2^{-1}$.
    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
    \[u_{2i+2,-}x+u_{2i+1,+}y=(u_{3,+}u_{2i,-}-u_{2,-}u_{2i-1,+})x+(u_{2,+}u_{2i,-}-u_{1,-}u_{2i-1,+})y\le u_{2j,-}\lambda_1+u_{2j-1,+}\lambda_2,\]
    which is the inequality (a) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
    \[-u_{2i+1,-}x-u_{2i,+}y=(-u_{3,+}u_{2i-1,-}+u_{2,-}u_{2i-2,+})x+(-u_{2,+}u_{2i-1,-}+u_{1,-}u_{2i-2,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (d) for $i+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
    \[u_{2i+3,-}x+u_{2i+2,+}y=(u_{3,+}u_{2i+1,-}-u_{2,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (b) for $i+1$.
    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_2^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
    \[-u_{2i+1,-}x-u_{2i,+}y=(u_{1,+}u_{2i-1,-}-u_{2,-}u_{2i,+})x+(-u_{0,+}u_{2i-1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (d) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_2^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
    \[-u_{2i+1,-}x+u_{2i+2,+}y=(-u_{1,+}u_{2i+1,-}+u_{0,-}u_{2i,+})x+(u_{2,+}u_{2i+1,-}-u_{1,-}u_{2i,+})y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which is the inequality (c) for $i+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
    \[-u_{2i+1,-}x-u_{2i,+}y\le u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,\]
    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
    This completes the induction on $i$, proving the Claim and the result for $k$ even.
